---
title: "Cleaning Temp Data"
author: "Camila Vargas"
date: "11/30/2021"
output: html_document
---

This scripts cleans csv files provided by Allie Hunter from Fish and Wildlife Service with Temperature data for Palmyra Atoll, data from SeaTempLoggers 2017.

Date range goes from"2014-07-18" to "2017-09-01"

The goal is to determine gaps un data collections and missing information needed to correctly document this data.

## Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## Load packages
library(here)
library(tidyverse)
library(janitor)

## Sets R not to use scientific notations
options(scipen=999) 

raw_data_path <- here::here("6.raw_data/")
```


## Read data
1. Create a tibble with all the csv that we need to read. Make sure to have a column with site name so we can keep track of this information.

```{r}
all_csv <- tibble(list.files(raw_data_path, pattern = ".csv")) %>% 
  rename(file_name = 1) %>%
  separate(col = file_name,
           into = c("site_name", "id2", "id3"),
           sep = "_",
           remove = FALSE) %>%
  filter(site_name != "SBE05604744") %>%  ## remove repeated file
  mutate(path = paste0(raw_data_path, "/", file_name),
         n = 1:n(),
         type = "temp") %>% 
  unite(obj_name, type, n, sep = "_", remove = FALSE) %>% 
  select(-id2, -id3)
```

2. Read each file

```{r}
## general funtion
read_csv_clean <- function(dataset){
  
  read_csv(dataset, skip = 11) %>% 
    clean_names()
}


for (i in all_csv$n){
  
  assign(all_csv$obj_name[i], read_csv_clean(all_csv$path[i]))
}

```

3. Check data

Both files from Eastern Flats (temp_3 and temp_4) are exactly the same.

temp_10 and temp_14 are the continuation of temp_9 and temp_13 respectively. This means we do not have to skip 11 rows, instead we need to read all and add colnames.

```{r}
all_equal(temp_3, temp_4) #True
setdiff(temp_3$temperature, temp_4$temperature)
setdiff(temp_3$date, temp_4$date)
setdiff(temp_4$date,temp_3$date)

colnames(temp_10)
colnames(temp_14)

```

4. Read temp_10 and temp_14 without skipping rows


```{r}
temp_10 <- read_csv(all_csv$path[10], col_names = F)

names(temp_10) <- c("sample_number","date","time","temperature")

temp_14 <- read_csv(all_csv$path[14], col_names = F)

names(temp_14) <- c("sample_number","date","time","temperature")

```



4. Combine all data and add site
```{r}

temp_list <- list(temp_1, temp_2, temp_3,temp_5, temp_6, temp_7, temp_8, temp_9, temp_10, temp_11, temp_12, temp_13, temp_14, temp_15, temp_16, temp_17, temp_18)

names(temp_list) <- c("temp_1", "temp_2", "temp_3", "temp_5", "temp_6", "temp_7", "temp_8", "temp_9", "temp_10", "temp_11", "temp_12", "temp_13", "temp_14", "temp_15", "temp_16", "temp_17", "temp_18")


all_temp <- bind_rows(temp_list, .id = "obj_name")


row_check <- all_temp %>% 
  group_by(obj_name) %>% 
  tally()


all_temp <- all_temp %>% 
  left_join(all_csv, by = "obj_name") %>% 
  select(-file_name, -path, -obj_name, -n, -type) %>% 
  mutate(year_folder = 2017)


```

Site names matches with names on Temperature Loggers Retrieved Aug 2017.xls

Need to check if all other information matches and determine gaps!
Plot data to see how it looks.


